I am applying for the Intern, Systems Engineering – Compute AI Hardware Platforms (Summer 2026) position at Graphcore. I am a Ph.D. student in Electrical Engineering and Computer Sciences (EECS) at the University of California, Berkeley, where my research focuses on integrating machine learning with system-level correctness, formal verification, and closed-loop control.

My work sits at the intersection of machine learning, systems engineering, and rigorous design methodologies. I develop techniques to transform and analyze learned models in ways that improve reliability, interpretability, and scalability when deployed in real systems. In particular, I have designed exact symbolic abstractions of neural-network controllers that enable scalable verification using SMT and MILP solvers, allowing precise reasoning about correctness under system-level constraints and uncertainty.

I am comfortable working across the ML systems stack, from model and algorithm design to implementation and large-scale evaluation. My research routinely involves building learning pipelines, benchmarking models, and analyzing trade-offs among performance, robustness, and computational cost—experience that aligns well with the challenges of evaluating and optimizing ML workloads on advanced AI hardware platforms.

I am excited by Graphcore’s mission to rethink AI compute through hardware–software co-design, and I would welcome the opportunity to contribute my background in ML, systems thinking, and verification-driven engineering to the development and evaluation of next-generation AI compute platforms.

Thank you very much for your time and consideration.
