%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\setlength\leftmargini{4ex}
\vspace{-2.0mm}

\begin{cvenumerates}

%---------------------------------------------------------
\item {\descriptionstyle{\descriptionhighlightstyle{Kevin Chang}, Nathan Dahlin, Rahul Jain, and Pierluigi Nuzzo, ``Equivalent and Compact Representations of Neural Network Controllers With Decision Trees,'' \emph{IEEE Transactions on Automatic Control}, pp.~1--14, 2026.}}

\item {\descriptionstyle{\descriptionhighlightstyle{Kevin Chang}, Nathan Dahlin, Rahul Jain, and Pierluigi Nuzzo, ``Exact and Cost-Effective Automated Transformation of Neural Network Controllers to Decision Tree Controllers,'' in \emph{Proc. IEEE Conference on Decision and Control (CDC)}, pp.~7843--7848, 2023.}}

\item {\descriptionstyle{Nathan Dahlin, \descriptionhighlightstyle{Kevin Chang}, K. C. Kalagarla, Rahul Jain, and Pierluigi Nuzzo, ``Practical Control Design for the Deep Learning Age: Distillation of Deep RL-Based Controllers,'' in \emph{Proc. Allerton Conference on Communication, Control, and Computing}, 2022.}}

\item {\descriptionstyle{Jair Certorio, \descriptionhighlightstyle{Kevin Chang}, Nuno C. Martins, Pierluigi Nuzzo, and Yasser Shoukry, ``Passivity Tools for Hybrid Learning Rules in Large Populations,'' \emph{Automatica}, 2026.}}

\item {\descriptionstyle{Wei-Kai Liu, Ming-Hung Chen, \descriptionhighlightstyle{Chia-Ming Chang}, Chen-Chia Chang, and Yao-Wen Chang, ``Time-Division Multiplexing Based System-Level FPGA Routing,'' in \emph{Proc. IEEE/ACM International Conference on Computer-Aided Design (ICCAD)}, 2021.}}
%---------------------------------------------------------
\end{cvenumerates}
\vspace{-2.0mm}
